---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rusfl

<!-- badges: start -->
<!-- badges: end -->

The goal of rusfl is to provide functions to load and parse USFL data.

## Installation

You can install the development version of rusfl from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mrcaseb/rusfl")
```

## NOTE

This USFL api requires an api key that is not provided with this package.

## Examples

### Load Basic Team Info

This will be loaded from Anthony Reinhard's Github.

```{r message=FALSE, warning=FALSE}
teams <- rusfl::usfl_load_teams()
dplyr::glimpse(teams)
```

### Load Game Info for multiple Weeks

The best way is to use the wrapper `rusfl::usfl_load_scores()` and choose the weeks. 

```{r message=FALSE, warning=FALSE}
games <- rusfl::usfl_load_scores(1:2)
dplyr::glimpse(games)
```

### Load Rosters

The best way is to use the wrapper `rusfl::usfl_load_rosters()` and choose the teams. The default loads all teams.

```{r message=FALSE, warning=FALSE}
roster <- rusfl::usfl_load_rosters()
roster
```

### Load Raw Game Data

Boxscores and Play by Play will be extracted from raw game data. So we have to load the raw game data first. The game ids are included in `games`. In this example these are 

```{r}
cli::cli_text("{games$id}")
```

Let's load `usfl3`

```{r message=FALSE, warning=FALSE}
raw <- rusfl::usfl_load_game_data("usfl3")
```

This will be a list of deeply nested lists. The structure is

```{r}
str(raw, max.level = 2)
```

Play by Play can be parsed with

```{r message=FALSE, warning=FALSE}
pbp <- rusfl::usfl_parse_pbp(raw)
dplyr::glimpse(pbp)
```

Boxscore data can be parsed on the player level or on the team level.

Team level will look like this

```{r message=FALSE, warning=FALSE}
rusfl::usfl_parse_boxscores(raw, "teams")
```

and player level will look like this

```{r message=FALSE, warning=FALSE}
player_stats <- rusfl::usfl_parse_boxscores(raw)
dplyr::glimpse(player_stats)
```
